% =====================================================================
%  Niloufar Modirshanehchi — Curriculum Vitae
%  Hand-authored LaTeX (pdflatex). No external CV class: the layout is
%  built from standard packages so the source is fully self-contained.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.6cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{array}
\usepackage[hidelinks]{hyperref}

% --- palette (kept consistent with the portfolio site) ----------------
\definecolor{ink}{HTML}{16203A}
\definecolor{accent}{HTML}{21409A}
\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\color{ink}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% --- section headings -------------------------------------------------
\titleformat{\section}
  {\large\bfseries\color{accent}}{}{0pt}{}[\vspace{1pt}\hrule height 0.8pt]
\titlespacing{\section}{0pt}{10pt}{6pt}

% --- helper: one experience entry ------------------------------------
% #1 role  #2 dates  #3 organisation/detail  #4 location
\newcommand{\entry}[4]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{2pt}}

\setlist[itemize]{leftmargin=1.2em, topsep=2pt, itemsep=1pt, parsep=0pt}

\begin{document}

% ----------------------------- header --------------------------------
\begin{center}
  {\LARGE\bfseries Niloufar Modirshanehchi}\\[4pt]
  (+49) 15757941944 \,$\cdot$\, Berlin, Germany \,$\cdot$\,
  \href{mailto:n.m.shanechi@gmail.com}{n.m.shanechi@gmail.com}\\[2pt]
  \href{https://github.com/PersianSpock}{github.com/PersianSpock} \,$\cdot$\,
  \href{https://www.linkedin.com/in/nil-modirshanehchi/}{linkedin.com/in/nil-modirshanehchi}
\end{center}

% --------------------------- education -------------------------------
\section{Education}
\entry{B.Sc. in Computer Science}{Sep. 2025 -- present}
      {Gisma University of Applied Sciences, Germany}{}
\begin{itemize}
  \item Pursuing a second B.Sc.
\end{itemize}
\vspace{4pt}
\entry{Associate's degree in Electrical Engineering}{2018 -- 2023}
      {Ferdowsi University of Mashhad, Iran}{}
\begin{itemize}
  \item Left the B.Sc. degree.
\end{itemize}

% ----------------------------- skills --------------------------------
\section{Skills}
\begin{tabular}{@{}>{\bfseries}p{3.4cm} p{14cm}@{}}
Programming Languages & Python, SQL, C++ \\[3pt]
Tools \& Libraries & Pandas, NumPy, PyTorch, TensorFlow, OpenCV, Scikit-Learn,
  LLM APIs, AWS (S3, SageMaker, EC2), Git, Docker \\[3pt]
Data Analytics & ETL/ELT Pipelines (Airflow, dbt), Data Warehousing
  (Snowflake, BigQuery), Data Lake Architectures, A/B Test Evaluation,
  User Behavior Analysis, Financial \& Operational Metric Analysis,
  Visualization Tools (Power BI, Tableau, Python libraries) \\[3pt]
Machine Learning & NLP Pipelines, LLM-based NLP Workflows, Transformer Models
  (Hugging Face), LLM Applications (RAG, API Integration), Recommender Systems,
  Feature Engineering, Model Evaluation \\[3pt]
Natural Languages & English (C1), German (A1 -- attending B1 intensive course) \\
\end{tabular}

% ------------------------ technical experience -----------------------
\section{Technical Experience}

\entry{Werkstudent Data Engineering}{May 2026 -- present}
      {thekey.academy (Working student)}{Berlin, Germany}
\begin{itemize}
  \item Working on analytics infrastructure and tracking quality across web,
        Android, and iOS platforms using BigQuery and GA4.
  \item Supporting data pipelines for ad platform data (Google Ads, Meta Ads)
        and cross-platform event tracking.
\end{itemize}
\vspace{5pt}

\entry{Junior Data Scientist}{Jul 2023 -- Sep 2023}
      {Hotelian.com (Full-time)}{Dubai, UAE}
\begin{itemize}
  \item Contributed to the development of a conversational AI platform for hotel
        bookings, presented at ITB Asia 2023, which focused on LLM-based content
        understanding, personalized recommendations, and search relevance.
  \item Built Data and NLP pipelines in Python and SQL over 1M+ user reviews,
        hotel metadata, and behavioral signals to learn reusable representations;
        replacing heuristic baseline with embedding-based ranking model,
        improving offline AUC from 0.68 $\to$ 0.75 (+10\% relative uplift) on
        user-level holdout; validated via a 2-week A/B test (CTR +4.7\%, $p<0.05$).
  \item Developed a personalized ranker using semantic embeddings, Elasticsearch,
        and GIS features; improving offline ranking (NDCG@10) from 0.31 to 0.37
        (+19\% relative) vs. the prior production ranker on a time-based
        validation set.
  \item Designed production KPIs and model monitoring (data quality, drift
        signals, conversion, latency, error rates) to track impact and
        reliability during rollouts.
\end{itemize}
\vspace{5pt}

\entry{Remote Research Intern}{Aug 2022 -- Jul 2023}
      {University College London (Internship)}{London, UK}
\begin{itemize}
  \item Worked on the core recommendation engine for personalization and ranking
        systems on a UCL-backed startup.
  \item Built a SQL feature extraction pipeline, and implemented contextual
        bandit ($\varepsilon$-greedy) for ranking optimization.
  \item Improved simulated NDCG@10 from 0.42 to 0.45 (+7\% relative) vs. an
        implicit MF baseline using offline replay evaluation.
  \item Produced end-to-end ML workflows on AWS (EC2, S3, SageMaker), reducing
        model iteration/training time by 10\%.
  \item Supported product decisions through model-driven content ranking
        experiments and A/B tests, and tracking conversion KPIs plus basic
        drift/data-quality checks after rollout.
\end{itemize}
\vspace{5pt}

\entry{Junior Data Analyst \& NLP Researcher}{July 2020 -- May 2023}
      {Wise Intelligent Agents (ahdsoft) (Part-time)}{Mashhad, Iran}
\textit{NLP Researcher:}
\begin{itemize}
  \item Built and deployed multiple NLP systems using pretrained transformer
        models (BERT, T5, TrOCR), leading supervised fine-tuning across OCR,
        ASR, and text classification tasks in low-resource Farsi, including
        CTC-based wav2vec2 adaptation and domain-specific tokenizer adaptation.
  \item Developed shared fine-tuning and evaluation pipelines for Farsi ASR,
        combining academic datasets (e.g., Common Voice) with large-scale
        proprietary data (recorded noisy conversations in Farsi); reducing WER by
        25--30\% (relative) vs. prior production models via systematic
        fine-tuning and data augmentation.
\end{itemize}
\textit{Junior Data Analyst:}
\begin{itemize}
  \item Delivered 150+ dashboards tracking revenue, cost, conversion, and
        operational KPIs across logistics, marketing, and sales, enabling
        data-driven decisions in budgeting, pricing, and operational planning.
  \item Developed and maintained ETL pipelines to transform raw data from data
        lake into structured warehouse schemas, improving data reliability and
        reporting efficiency, reducing query time and storage costs.
  \item Performed EDA workflows, customer segmentation, and user-behavior
        analysis for supporting targeted marketing and content strategies,
        leading to conversion improvements.
  \item Collaborated with product and business stakeholders to define KPIs and
        perform analysis on trade-offs between growth, customer acquisition
        efficiency, and operational costs.
\end{itemize}
\vspace{5pt}

\entry{Remote Research Intern}{July 2021 -- Sep. 2021}
      {Dublin City University (Internship)}{Dublin, Ireland}
\begin{itemize}
  \item Contributed to a research project on Graph Neural Networks (GNNs) aimed
        at extracting structured knowledge from deep neural networks and
        generating human-readable local explanations.
  \item Developed and implemented semantic knowledge graph models using Neo4j
        while utilizing Python, PyTorch, and TensorFlow on CIFAR-10 and
        CIFAR-100 datasets.
  \item Supported research efforts through practical ML implementations, laying a
        strong foundation in advanced neural network techniques.
\end{itemize}

% ---------------------------- activities -----------------------------
\section{Activities}
\begin{itemize}
  \item Olympiad teacher for high school students (Combinatorics, Advanced
        Algorithms, Graph Theory) --- 2018--2021.
  \item Problem Setter \& Judge at 16th International ISC Conference on
        Information Security and Cryptology (ISCISC'19) --- 2019.
  \item Problem Setter \& Judge for state-wide Mathematics Olympiad for middle
        school students --- 2018.
\end{itemize}

\end{document}
